### 2022-03-16 sections/systematic_uncertainties.tex

The statistical uncertainties on the fake tau background calibration in the leptonic channel are applied with uncorrelated uncertainties for
different fake tau sources and different $\pt$ slices. The uncertainties on the MC modelling of the various processes that used for
evaluating the fake factors in the CRs are considered and treated fully correlated.
The uncertainty of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both,
its statistical fluctuation and the differences between the leptonic channels.
The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs. The uncertainties on the MC modelling of the various processes that used for
evaluating the fake factors in the CRs are treated fully correlated in the fit.

@@

Several normalisation and shape uncertainties are taken into account and are treated fully correlated for the $\Hq$ and $pp\to tH$ signals.
Uncertainties of the Higgs boson branching ratios are taken from the measured values in Ref.~\cite{Zyla:2020zbs}.
%into account following the recommendation in Ref.~\cite{deFlorian:2016spz}.
The uncertainty of ISR, FSR, scale and PDF are considered and are treated fully correlated in all SRs. The parton shower uncertainties are estimated by comparing
the nominal to an alternative sample interfaced with {\herwig7}.
%the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}. 
%treated correlatedly with $\ttbar$ samples.

>>>>

The statistical uncertainties on the fake tau background calibration in the leptonic channel are applied with uncorrelated uncertainties for
different fake tau sources and different $\pt$ slices. The uncertainties on the MC modelling of the various processes used for
evaluation of the fake factors in the CRtt's are considered and treated as fully correlated in the fit.
The uncertainty of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both,
its statistical fluctuation and the differences between the leptonic channels.
The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factorsderived from different signal depleted CRs.
%The uncertainties on the MC modelling of the various processes used for
%evaluation of the fake factors in the CRtt's are treated as fully correlated in the fit.

@@

Several normalisation and shape uncertainties are taken into account and are treated as fully correlated for the $\Hq$ and $pp\to tH$ signals.
Uncertainties of the Higgs boson branching ratios are taken from the measured values in Ref.~\cite{Zyla:2020zbs}.
%into account following the recommendation in Ref.~\cite{deFlorian:2016spz}.
The uncertainty of ISR, FSR, scale and PDF are considered and are treated fully correlated in all SRs. The parton shower uncertainties are estimated by comparing
the nominal to an alternative sample interfaced with {\herwig7}.
%the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}. 
%treated correlatedly with $\ttbar$ samples.
